% Extracurricular Activities
\section{Extracurricular Activities}
% Institutional Representation & Teamwork
\denseouterlist{
\entrymid[\textbullet]
{\textbf{Athletic Representative} - FES Acatl치n UNAM}{2023\textendash 2024}
{Selected to represent prestigious FES Acatl치n in CONDE football tournament and TESCI soccer competitions. Balanced competitive sports with academic excellence. \textit{Demonstrates: Institutional trust, team collaboration, time management.}}

% Strategic Analysis & Decision Making
\entrymid[\textbullet]
{\textbf{Chess Team Strategist} - FES Acatl치n}{2023}
{Member of institutional chess team developing advanced strategic thinking and analytical problem-solving skills. Discontinued due to prioritization of core academic and research commitments. \textit{Demonstrates: Strategic mindset, logical analysis, mature prioritization.}}

% Endurance & Cultural Exploration
\entrymid[\textbullet]
{\textbf{Competitive Cyclist \& Cultural Explorer}}{2020\textendash Current}
{Active competitive cyclist with extensive exploration across Mexican Republic. Combine physical endurance challenges with cultural discovery and geographical knowledge expansion. \textit{Demonstrates: Mental resilience, curiosity, adventure-driven learning.}}

% Cross-Cultural Communication & Technical Storytelling
\entrymid[\textbullet]
{\textbf{Technical Content Creator \& Cultural Bridge-Builder}}{2023\textendash Current}
{Created multilingual technical blog exploring intersection of technology, human psychology, and adventure. Focus on democratizing cybersecurity knowledge and fostering cross-cultural tech communication. \textit{Demonstrates: Communication excellence, cultural intelligence, humanistic technology vision.}}
}

% Professional Personality Analysis Section
\section{Leadership \& Personality Profile}
\denseouterlist{
% Competitive Excellence & Results-Oriented Mindset  
\entry{\textbullet\ \textbf{Performance-Driven:} 2nd place achievement in competitive programming showcases winning mentality and ability to deliver results under pressure}

% Institutional Trust & Professional Representation
\entry{\textbullet\ \textbf{Institutional Confidence:} Selected to represent FES Acatl치n UNAM in competitive sports demonstrates institutional trust and professional representation capabilities}

% Strategic Thinking & Analytical Problem-Solving
\entry{\textbullet\ \textbf{Strategic Analyst:} Chess team experience and competitive programming success highlight advanced strategic thinking and systematic problem-solving approach}

% Mental Resilience & Endurance Under Challenge
\entry{\textbullet\ \textbf{Mental Resilience:} Competitive cycling across Mexico demonstrates exceptional mental endurance, physical discipline, and challenge-seeking mindset}

% Cross-Cultural Communication & Humanistic Technology Vision
\entry{\textbullet\ \textbf{Cultural Intelligence:} Multilingual blog creation and cross-cultural technology focus showcase advanced communication skills and humanistic approach to technology}

% Balanced Prioritization & Time Management Excellence
\entry{\textbullet\ \textbf{Strategic Prioritization:} Ability to balance multiple high-level commitments while maintaining academic excellence (GPAs 91.7 \& 85.6) demonstrates superior time management}
}